Mistriage

### 2019-05-20 ManuscriptMarkdown.Rmd
Update ManuscriptMarkdown.Rmd

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
## LOADING ENVIROMENT AND TABLES
results <- readRDS("compiled output/original.results.Rds")
result.tables <- readRDS("result.tables.Rds")
# table.one <-

## PREPARED CODE
## Total patients and NA
total.number.of.patients <- nrow(results$data.sets.before.imputations$multi.centre.vs.single.centre$multi.centre)
total.number.of.na <- results$NA.info.sample$multi.centre.vs.single.centre$multi.centre$total.number.of.na
## Sample NA
na.vector <- unlist(results$NA.info.sample)
highest.percent.missing.number <- max(na.vector[na.vector<100])
highest.percent.missing.name <- names((na.vector[na.vector == highest.percent.missing.number]))
## Variable NA
number.variable.na <- max(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na)
percent.variable.na <- results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$percentage[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na]
name.variable.na <- row.names( results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na,] )
gcs.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_gcs_sum",])
sbp.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_sbp_value",])
## Development and validation
high.low.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "high.volume"]
metro.non.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "metropolitan"]
multi.single.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "multi.centre"]
max.imp <- max(results$original.stats$Total.imputations)
best.validation <- results$original.stats[results$original.stats$Validation.mistriage.median == min(results$original.stats$Validation.mistriage.median),]
## Comparison
best.transfer <- results$original.stats[results$original.stats$Transfer.mistriage.median == min(results$original.stats$Transfer.mistriage.median),]
worst.transfer <- results$original.stats[results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median == max(results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median),]
## Figure and table setup
# Figure 1 = Figure 1: High- and low volume centre data set. Initial split based on number of patients. Temporal split made using date of traumatic event.
# Table 1 = Sample characteristics table
# Table 2 = result.tables, cropped to only show validation
# Table 3 = Cropped to only show transfer
# Table 4 = Cropped to only show transfer differance
```
# Introduction
Trauma results in millions of deaths annually across the globe, and road traffic injuries are among the top 10 leading causes of death worldwide (1, 2). Each year 9% of the world’s deaths are because of trauma, and predictions indicate that this number is likely to increase (3).

@@

```{r, echo = FALSE, results = "asis"} 
## Figure 1 = Figure 1: High- and low volume centre data set. Initial split based on number of patients. Temporal split made using date of traumatic event. 
```

@@

```{r, echo = FALSE, results = "asis"} 
## Table 1 = Sample characteristics table
##result.tables
```

@@

```{r, echo = FALSE, results = "asis"} 
## Table 2 = Cropped to only show validation
result.tables
```

@@

```{r, echo = FALSE, results = "asis"} 
## Table 3 = Cropped to only show transfer
result.tables
```

@@

```{r, echo = FALSE, results = "asis"} 
## Table 4 = Cropped to only show transfer differance
result.tables
```

>>>>

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
## LOADING ENVIROMENT AND TABLES
## Original results and UI tables
results <- readRDS("output/original.results.Rds")
result.tables <- readRDS("result.tables.Rds")
result.tables.data.frame <- readRDS("result.tables.data.frame.Rds")
## Sample characteristics table
# table.one <-

## PREPARED CODE
## Total patients and NA
total.number.of.patients <- nrow(results$data.sets.before.imputations$multi.centre.vs.single.centre$multi.centre)
total.number.of.na <- results$NA.info.sample$multi.centre.vs.single.centre$multi.centre$total.number.of.na
## Sample NA
na.vector <- unlist(results$NA.info.sample)
highest.percent.missing.number <- max(na.vector[na.vector<100])
highest.percent.missing.name <- names((na.vector[na.vector == highest.percent.missing.number]))
## Variable NA
number.variable.na <- max(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na)
percent.variable.na <- results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$percentage[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na]
name.variable.na <- row.names( results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[results$NA.info.variable$multi.centre.vs.single.centre$multi.centre$number.of.na == number.variable.na,] )
gcs.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_gcs_sum",])
sbp.na <- (results$NA.info.variable$multi.centre.vs.single.centre$multi.centre[row.names(results$NA.info.variable$multi.centre.vs.single.centre$multi.centre) == "ed_sbp_value",])
## Development and validation
high.low.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "high.volume"]
metro.non.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "metropolitan"]
multi.single.imp <- results$original.stats$Total.imputations[results$original.stats$Sample.name == "multi.centre"]
max.imp <- max(results$original.stats$Total.imputations)
best.validation <- results$original.stats[results$original.stats$Validation.mistriage.median == min(results$original.stats$Validation.mistriage.median),]
## Comparison
best.transfer <- results$original.stats[results$original.stats$Transfer.mistriage.median == min(results$original.stats$Transfer.mistriage.median),]
worst.transfer <- results$original.stats[results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median == max(results$original.stats$Transferred.mistriage.minus.buddy.local.mistriage.median),]

## Table setup
# Table 1 = Sample characteristics table
#
# Table 2 = result.tables, cropped to only show validation
table.2 <- lapply(result.tables.data.frame, function(x) x[1:3,])
table.2 <- lapply(table.2, function(result) {
           kable(result, format = "markdown")
           })
# Table 3 = Cropped to only show transfer
table.3 <- lapply(result.tables.data.frame, function(x) x[4:6,])
table.3 <- lapply(table.3, function(result) {
           kable(result, format = "markdown")
           })
# Table 4 = Cropped to only show transfer differance
table.4 <- lapply(result.tables.data.frame, function(x) x[7:9,])
table.4 <- lapply(table.4, function(result) {
           kable(result, format = "markdown")
           })
```
# Introduction
Trauma results in millions of deaths annually across the globe, and road traffic injuries are among the top 10 leading causes of death worldwide (1, 2). Each year 9% of the world’s deaths are because of trauma, and predictions indicate that this number is likely to increase (3).

@@

![**Figure 1** High- and low volume centre data set. Initial split based on number of patients. Temporal split made using date of traumatic event.](fig1.jpg)

@@

```{r, echo = FALSE, results = "asis"} 
## Table 1 = Sample characteristics table
#
```

@@

```{r, echo = FALSE, results = "asis"} 
## Table 2 = Cropped to only show validation
table.2
```

@@

```{r, echo = FALSE, results = "asis"} 
## Table 3 = Cropped to only show transfer
table.3
```

@@

```{r, echo = FALSE, results = "asis"} 
## Table 4 = Cropped to only show transfer differance
table.4
```
